\documentclass[8pt,aspectratio=169]{beamer}
\usetheme{Madrid}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{adjustbox}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{amssymb}

% Color definitions
\definecolor{mlblue}{RGB}{0,102,204}
\definecolor{mlpurple}{RGB}{51,51,178}
\definecolor{mllavender}{RGB}{173,173,224}
\definecolor{mllavender2}{RGB}{193,193,232}
\definecolor{mllavender3}{RGB}{204,204,235}
\definecolor{mllavender4}{RGB}{214,214,239}
\definecolor{mlorange}{RGB}{255, 127, 14}
\definecolor{mlgreen}{RGB}{44, 160, 44}
\definecolor{mlred}{RGB}{214, 39, 40}
\definecolor{mlgray}{RGB}{127, 127, 127}

% Additional colors
\definecolor{lightgray}{RGB}{240, 240, 240}
\definecolor{midgray}{RGB}{180, 180, 180}

% Apply custom colors to Madrid theme
\setbeamercolor{palette primary}{bg=mllavender3,fg=mlpurple}
\setbeamercolor{palette secondary}{bg=mllavender2,fg=mlpurple}
\setbeamercolor{palette tertiary}{bg=mllavender,fg=white}
\setbeamercolor{palette quaternary}{bg=mlpurple,fg=white}

\setbeamercolor{structure}{fg=mlpurple}
\setbeamercolor{section in toc}{fg=mlpurple}
\setbeamercolor{subsection in toc}{fg=mlblue}
\setbeamercolor{title}{fg=mlpurple}
\setbeamercolor{frametitle}{fg=mlpurple,bg=mllavender3}
\setbeamercolor{block title}{bg=mllavender2,fg=mlpurple}
\setbeamercolor{block body}{bg=mllavender4,fg=black}

% Remove navigation symbols
\setbeamertemplate{navigation symbols}{}

% Clean itemize/enumerate
\setbeamertemplate{itemize items}[circle]
\setbeamertemplate{enumerate items}[default]

% Reduce margins for more content space
\setbeamersize{text margin left=5mm,text margin right=5mm}

% Command for bottom annotation
\newcommand{\bottomnote}[1]{%
\vfill
\vspace{-2mm}
\textcolor{mllavender2}{\rule{\textwidth}{0.4pt}}
\vspace{1mm}
\footnotesize
\textbf{#1}
}

% Command for compact list spacing
\newcommand{\compactlist}{%
\setlength{\itemsep}{0pt}%
\setlength{\parskip}{0pt}%
\setlength{\parsep}{0pt}%
}

% Notation macros
\input{../notation}

\title{Quiz: Search Protocol}
\subtitle{AI-Based Detection of Hedge Fund Fraud}
\author{Joerg Osterrieder}
\institute{Zurich University of Applied Sciences (ZHAW)}
\date{2025}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Question 1}
What search period does the systematic review cover?
\begin{itemize}\compactlist
\item[a)] 2010--2024
\item[b)] 2005--2025
\item[c)] 2000--2025
\item[d)] 2015--2025
\end{itemize}

\pause
\begin{block}{Answer}
\textbf{c)} 2000--2025\\[2mm]
The systematic review covers a 25-year period from 2000 to 2025, capturing the evolution of AI-based fraud detection from early statistical methods to modern deep learning approaches.
\end{block}
\bottomnote{Appendix A0: Search Protocol}
\end{frame}

\begin{frame}{Question 2}
What is the citation threshold for including preprints?
\begin{itemize}\compactlist
\item[a)] 10 citations
\item[b)] 20 citations
\item[c)] 50 citations
\item[d)] No threshold
\end{itemize}

\pause
\begin{block}{Answer}
\textbf{b)} 20 citations\\[2mm]
Preprints (arXiv, SSRN) were included only if they had at least 20 citations, ensuring they represent influential work despite not being peer-reviewed. This balances currency with quality.
\end{block}
\bottomnote{Appendix A0: Inclusion Criteria}
\end{frame}

\begin{frame}{Question 3}
How many independent reviewers conducted the screening process?
\begin{itemize}\compactlist
\item[a)] 1
\item[b)] 2
\item[c)] 3
\item[d)] 5
\end{itemize}

\pause
\begin{block}{Answer}
\textbf{b)} 2\\[2mm]
Two independent reviewers conducted title/abstract screening and full-text assessment. Disagreements were resolved through discussion or consultation with a third reviewer, following best practices for systematic reviews.
\end{block}
\bottomnote{Appendix A0: Quality Assurance}
\end{frame}

\begin{frame}{Question 4}
What technique identified additional studies beyond database searches?
\begin{itemize}\compactlist
\item[a)] Expert consultation
\item[b)] Social media
\item[c)] Conference attendance
\item[d)] Snowballing
\end{itemize}

\pause
\begin{block}{Answer}
\textbf{d)} Snowballing\\[2mm]
Backward snowballing (reviewing reference lists) and forward snowballing (checking citations of key papers) identified additional relevant studies missed by database searches, ensuring comprehensive coverage.
\end{block}
\bottomnote{Appendix A0: Supplementary Search}
\end{frame}

\end{document}
