\documentclass[8pt,aspectratio=169]{beamer}
\usetheme{Madrid}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{adjustbox}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{amssymb}

% Color definitions
\definecolor{mlblue}{RGB}{0,102,204}
\definecolor{mlpurple}{RGB}{51,51,178}
\definecolor{mllavender}{RGB}{173,173,224}
\definecolor{mllavender2}{RGB}{193,193,232}
\definecolor{mllavender3}{RGB}{204,204,235}
\definecolor{mllavender4}{RGB}{214,214,239}
\definecolor{mlorange}{RGB}{255, 127, 14}
\definecolor{mlgreen}{RGB}{44, 160, 44}
\definecolor{mlred}{RGB}{214, 39, 40}
\definecolor{mlgray}{RGB}{127, 127, 127}

% Additional colors
\definecolor{lightgray}{RGB}{240, 240, 240}
\definecolor{midgray}{RGB}{180, 180, 180}

% Apply custom colors to Madrid theme
\setbeamercolor{palette primary}{bg=mllavender3,fg=mlpurple}
\setbeamercolor{palette secondary}{bg=mllavender2,fg=mlpurple}
\setbeamercolor{palette tertiary}{bg=mllavender,fg=white}
\setbeamercolor{palette quaternary}{bg=mlpurple,fg=white}

\setbeamercolor{structure}{fg=mlpurple}
\setbeamercolor{section in toc}{fg=mlpurple}
\setbeamercolor{subsection in toc}{fg=mlblue}
\setbeamercolor{title}{fg=mlpurple}
\setbeamercolor{frametitle}{fg=mlpurple,bg=mllavender3}
\setbeamercolor{block title}{bg=mllavender2,fg=mlpurple}
\setbeamercolor{block body}{bg=mllavender4,fg=black}

% Remove navigation symbols
\setbeamertemplate{navigation symbols}{}

% Clean itemize/enumerate
\setbeamertemplate{itemize items}[circle]
\setbeamertemplate{enumerate items}[default]

% Reduce margins for more content space
\setbeamersize{text margin left=5mm,text margin right=5mm}

% Command for bottom annotation
\newcommand{\bottomnote}[1]{%
\vfill
\vspace{-2mm}
\textcolor{mllavender2}{\rule{\textwidth}{0.4pt}}
\vspace{1mm}
\footnotesize
\textbf{#1}
}

% Command for compact list spacing
\newcommand{\compactlist}{%
\setlength{\itemsep}{0pt}%
\setlength{\parskip}{0pt}%
\setlength{\parsep}{0pt}%
}

% Notation macros
\input{../notation}

\title{Quiz: Introduction to AI-Based Detection of Hedge Fund Fraud}
\subtitle{Section 01 -- Digital-AI-Finance}
\author{Joerg Osterrieder}
\institute{Zurich University of Applied Sciences (ZHAW)}
\date{2025}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Question 1: Global Hedge Fund AUM}
What is the approximate AUM of the global hedge fund industry as of 2025?

\vspace{0.5cm}
\begin{enumerate}[a)]
\item \$2.0 trillion
\item \$3.5 trillion
\item \$4.5 trillion
\item \$6.0 trillion
\end{enumerate}

\vspace{0.5cm}
\pause
\begin{block}{Answer}
\textbf{c) \$4.5 trillion}

The global hedge fund industry manages assets exceeding \$4.5 trillion as of 2025, having grown substantially from roughly \$2 trillion at the onset of the 2008 financial crisis.
\end{block}
\bottomnote{Source: Section 1.1}
\end{frame}

\begin{frame}{Question 2: Madoff Losses}
What were the estimated losses from the Madoff Ponzi scheme?

\vspace{0.5cm}
\begin{enumerate}[a)]
\item \$10 billion
\item \$35 billion
\item \$65 billion
\item \$100 billion
\end{enumerate}

\vspace{0.5cm}
\pause
\begin{block}{Answer}
\textbf{c) \$65 billion}

The collapse of Bernard L. Madoff Investment Securities in December 2008 revealed a Ponzi scheme with estimated losses of \$65 billion in stated account value, making it the largest financial fraud in history.
\end{block}
\bottomnote{Source: Section 1.1}
\end{frame}

\begin{frame}{Question 3: AI/ML Advantages}
Which of these is NOT one of the four advantages of AI/ML for fraud detection?

\vspace{0.5cm}
\begin{enumerate}[a)]
\item Scalability
\item Real-time monitoring
\item Cost reduction
\item Multi-modal integration
\end{enumerate}

\vspace{0.5cm}
\pause
\begin{block}{Answer}
\textbf{c) Cost reduction}

The four fundamental advantages are: (1) scalability, (2) pattern recognition, (3) real-time monitoring, and (4) multi-modal data integration. Cost reduction is not listed as a primary advantage.
\end{block}
\bottomnote{Source: Section 1.2}
\end{frame}

\begin{frame}{Question 4: Principal Contributions}
How many principal contributions does this survey make?

\vspace{0.5cm}
\begin{enumerate}[a)]
\item 2
\item 3
\item 4
\item 5
\end{enumerate}

\vspace{0.5cm}
\pause
\begin{block}{Answer}
\textbf{b) 3}

The survey makes three principal contributions: C1 (Detection Pipeline Taxonomy), C2 (Adversarial and Regulatory Readiness Assessment), and C3 (Actionable Research Roadmap).
\end{block}
\bottomnote{Source: Section 1.3}
\end{frame}

\begin{frame}{Question 5: Why No Meta-Analysis?}
Why does this survey NOT conduct a quantitative meta-analysis?

\vspace{0.5cm}
\begin{enumerate}[a)]
\item Insufficient data
\item Heterogeneity of datasets, metrics, and definitions
\item Legal restrictions
\item Time constraints
\end{enumerate}

\vspace{0.5cm}
\pause
\begin{block}{Answer}
\textbf{b) Heterogeneity of datasets, metrics, and definitions}

A qualitative synthesis approach is adopted because the heterogeneity of datasets, fraud definitions, evaluation protocols, and reporting standards across the existing literature precludes meaningful statistical aggregation.
\end{block}
\bottomnote{Source: Section 1.3}
\end{frame}

\begin{frame}{Question 6: SEC Staffing}
Approximately how many staff does the SEC employ?

\vspace{0.5cm}
\begin{enumerate}[a)]
\item 1,200
\item 2,800
\item 4,600
\item 8,500
\end{enumerate}

\vspace{0.5cm}
\pause
\begin{block}{Answer}
\textbf{c) 4,600}

The SEC employs approximately 4,600 staff to oversee thousands of registered investment advisers, broker-dealers, and fund complexes, creating a stark mismatch between regulatory capacity and industry scale.
\end{block}
\bottomnote{Source: Section 1.2}
\end{frame}

\end{document}
